Stack Safety is a Security Property

### 2021-04-17 tex/main.tex

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
If \(f\) is a predicate on machine states, we define \(\mpcstatename
\hookrightarrow \MPCT | f\) (read ``\(\MPCT\) is the prefix of
running \(\mpcstatename\) up to \(f\)''):
%
\begin{center}
\judgmenttwo{\(\mpcstatename \hookrightarrow \MPCT'\)}
%            {\(\PUT ~ f ~ \mpcstatename ~ \MPCT' = \MPCT\)}
            {\(\PUT ~ f ~ \MPCT' = \MPCT\)}
            {\(\mpcstatename \hookrightarrow \MPCT | f\)}
\end{center}
\apt{above changed: SNA please check.}

@@

\definition
A system enjoys \textbf{\textit{stepwise stack confidentiality}} if,
for any \(\MPCT,\brk \in \MPCT^*\) with \(\head(\MPCT) = \mach,\pol,\context\),
any \(\nach\) such that \(\mach \approx_{\mathit{secret}(\context)} \nach\), and any trace
%\(\NPCT\) such that \(\nach,\pol,\domMap \hookrightarrow \NPCT | \brk\),
\(\NPCT\) such that \(\nach,\pol,\context \hookrightarrow \NPCT | \brk\),
\(\MPCT \doteq \NPCT\) holds.
\apt{changed $dm$ to $ctx$; SNA please check.}

@@

10  f:   add $1,%sp          ; allocate frame
11       mov -3(%sp),-1(%sp) ; y = a
12       mul $2,-1(%sp)      ; y = a*2
13       mov $0,-3(%sp)      ; a = 0
14       sub $1,%sp          ; deallocate frame
15       ret
\end{verbatim}
}
  \end{subfigure}
\begin{subfigure}{.65\textwidth}
\vspace*{0.2in}
\begin{center}
\begin{tabular}{l r | l}
  {\tt 3} &
  \multicolumn{2}{c}{
    \memoryaddrs[(0)]{8em}
    \memory{4}{\unsealc}
    ~$\cdots$
    \MemoryLabel{-19em}{0.75em}{5}
%    \MemoryLabel{-14em}{0.75em}{0}
%    \MemoryLabel{-10em}{0.75em}{0}
%    \MemoryLabel{-7em}{0.75em}{0}
    \vspace{.5em}
  } \\
  {\tt 11} &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}[Seal(0)]%
  \memory{1}{\mainpassc}[P(0,1)]%
  \memory{1}{\retptrc}[RetPtr]%
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{5}
  \MemoryLabel{-14em}{0.75em}{5}
%  \MemoryLabel{-6em}{0.75em}{0}
  &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{\(v_0\)}
  \MemoryLabel{-14em}{0.75em}{5}
  \MemoryLabel{-6em}{0.75em}{\(v_1\)}
  \\
  {\tt 13} &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{5}
  \MemoryLabel{-14em}{0.75em}{5}
  \MemoryLabel{-6em}{0.75em}{10}
  &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{\(v_0\)}
  \MemoryLabel{-14em}{0.75em}{5}
  \MemoryLabel{-6em}{0.75em}{10}
  \\
  {\tt 14} &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{5}
  \MemoryLabel{-14em}{0.75em}{0}
  \MemoryLabel{-6em}{0.75em}{10}
  &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{\(v_0\)}
  \MemoryLabel{-14em}{0.75em}{0}
  \MemoryLabel{-6em}{0.75em}{10}
  \\
  \\
  {\tt 8} &
  \multicolumn{2}{c}{
    \memoryaddrs[(0)]{8em}
    \memory{4}{\unsealc}
    ~$\cdots$
    \MemoryLabel{-19em}{0.75em}{10}
    \MemoryLabel{-14em}{0.75em}{0}
    \MemoryLabel{-10em}{0.75em}{\#6}
    \MemoryLabel{-7em}{0.75em}{10}
    \vspace{.5em}
  } \\
\end{tabular}
\end{center}

@@

20 f:     cmp stash, $0   ; stash = 0?
21        breq #13        ; branch if so
22        mov %ra,stash   ; stash = &a
23        jmp #15
24        mov $5, (stash) ; *stash = 5
25        ret
}
\end{verbatim}
}
  \end{subfigure}
  \begin{subfigure}[t]{.29\textwidth}
    \begin{center}
    \begin{tabular}{l l}
      {\tt 20} &
      \memoryaddrs[(1)]{17em}
      \memory{1}{\mainpassc}[{\makebox[0pt]{P(0,1)}}]%
      \memory{1}{\mainsealc}[{\makebox[0pt]{Seal(0)}}]%
      \memory{1}{\retptrc}
%      \memory{1}{\unsealc}
      ~$\cdots$ \\
      {\tt 25} &
      \memoryaddrs[(1)]{17em}
      \memory{1}{\mainpassc}
      \memory{1}{\mainsealc}
      \memory{1}{\retptrc}
%      \memory{1}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-18em}{0.75em}{5}
      \\
      {\tt 8} &
      \memoryaddrs[(0)]{12em}
      \memory{3}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-18em}{0.75em}{0}
      \\
      {\tt 20} &
      \memoryaddrs[(1)]{17em}
      \memory{1}{\mainsealc}[{\makebox[0pt]{Seal(0)}}]%
      \memory{1}{\mainpassc}[{\makebox[0pt]{P(0-1)}}]%
      \memory{1}{\retptrc}
%      \memory{1}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-18em}{0.75em}{0}
      \\
      {\tt 25} &
      \memoryaddrs[(1)]{17em}
      \memory{1}{\mainsealc}
      \memory{1}{\mainpassc}
      \memory{1}{\retptrc}
%      \memory{1}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-18em}{0.75em}{\bf 5}
\end{tabular}
\end{center}
\vspace{\abovedisplayskip}
\end{subfigure}
\caption{A violation with pass-by-reference}
\label{fig:passing}
\end{figure}

@@

Although there are some important differences between
\citeauthor{SkorstengaardSTK}'s properties and our own, the new
properties arguably satisfy their list of desiderata for such
formulations: notably, they reflect (and refine) programmer intuitions
about stack safety, furnish a comprehensive picture of the meaning of
stack safety, can be used to reason about program behavior, and are
flexible enough to be allow extensions to richer settings.
%
\sna{Some of this seems like more detail than we need, and we need to
  compare ourselves to their list of criteria.}
\rb{Trimmed this a bit. Are you referring to their list of attack
  examples, or to something else?\apt{Their list at start of section 4.
  \rb{Had a go at this.}}}

>>>>

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
If \(f\) is a predicate on machine states, we define \(\mpcstatename
\hookrightarrow \MPCT | f\) (read ``\(\MPCT\) is the prefix of
running \(\mpcstatename\) up to \(f\)''):
%
\begin{center}
\judgmenttwo{\(\mpcstatename \hookrightarrow \MPCT'\)}
            {\(\PUT ~ f ~ \MPCT' = \MPCT\)}
            {\(\mpcstatename \hookrightarrow \MPCT | f\)}
\end{center}

@@

\definition
A system enjoys \textbf{\textit{stepwise stack confidentiality}} if,
for any \(\MPCT,\brk \in \MPCT^*\) with \(\head(\MPCT) = \mach,\pol,\context\),
any \(\nach\) such that \(\mach \approx_{\mathit{secret}(\context)} \nach\), and any trace
%\(\NPCT\) such that \(\nach,\pol,\domMap \hookrightarrow \NPCT | \brk\),
\(\NPCT\) such that \(\nach,\pol,\context \hookrightarrow \NPCT | \brk\),
\(\MPCT \doteq \NPCT\) holds.

@@

10  f:   add $1,%sp          ; allocate frame
11       mov -3(%sp),-1(%sp) ; y = a
12       mul $2,-1(%sp)      ; y = a*2
13       mov $0,-3(%sp)      ; a = 0
14       sub $1,%sp          ; deallocate frame
15       ret
\end{verbatim}
}
  \end{subfigure}
\begin{subfigure}{.65\textwidth}
\vspace*{0.2in}
\begin{center}
\begin{tabular}{l r | l}
  {\tt 3} &
  \multicolumn{2}{c}{
    \memoryaddrs[(0)]{8em}
    \memory{4}{\unsealc}
    ~$\cdots$
    \MemoryLabel{-19em}{0.75em}{5}
%    \MemoryLabel{-14em}{0.75em}{0}
%    \MemoryLabel{-10em}{0.75em}{0}
%    \MemoryLabel{-7em}{0.75em}{0}
    \vspace{.5em}
  } \\
  {\tt 11} &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}[S(0)]%
  \memory{1}{\mainpassc}[P(0,1)]%
  \memory{1}{\retptrc}[RetPtr]%
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{5}
  \MemoryLabel{-14em}{0.75em}{5}
%  \MemoryLabel{-6em}{0.75em}{0}
  &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{\(v_0\)}
  \MemoryLabel{-14em}{0.75em}{5}
  \MemoryLabel{-6em}{0.75em}{\(v_1\)}
  \\
  {\tt 13} &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{5}
  \MemoryLabel{-14em}{0.75em}{5}
  \MemoryLabel{-6em}{0.75em}{10}
  &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{\(v_0\)}
  \MemoryLabel{-14em}{0.75em}{5}
  \MemoryLabel{-6em}{0.75em}{10}
  \\
  {\tt 14} &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{5}
  \MemoryLabel{-14em}{0.75em}{0}
  \MemoryLabel{-6em}{0.75em}{10}
  &
  \memoryaddrs[(1)]{21.5em}
  \memory{1}{\mainsealc}
  \memory{1}{\mainpassc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{\(v_0\)}
  \MemoryLabel{-14em}{0.75em}{0}
  \MemoryLabel{-6em}{0.75em}{10}
  \\
  \\
  {\tt 8} &
  \multicolumn{2}{c}{
    \memoryaddrs[(0)]{8em}
    \memory{4}{\unsealc}
    ~$\cdots$
    \MemoryLabel{-19em}{0.75em}{10}
    \MemoryLabel{-14em}{0.75em}{0}
    \MemoryLabel{-10em}{0.75em}{\#6}
    \MemoryLabel{-7em}{0.75em}{10}
    \vspace{.5em}
  } \\
\end{tabular}
\end{center}

@@

20 f:     cmp stash, $0   ; stash = 0?
21        breq #13        ; branch if so
22        mov %ra,stash   ; stash = &a
23        jmp #15
24        mov $5, (stash) ; *stash = 5
25        ret
}
\end{verbatim}
}
  \end{subfigure}
  \begin{subfigure}[t]{.29\textwidth}
    \begin{center}
    \begin{tabular}{l l}
      {\tt 20} &
      \memoryaddrs[(1)]{17em}
      \memory{1}{\mainpassc}[{\makebox[0pt]{P(0,1)}}]%
      \memory{1}{\mainsealc}[{\makebox[0pt]{S(0)}}]%
      \memory{1}{\retptrc}
%      \memory{1}{\unsealc}
      ~$\cdots$ \\
      {\tt 25} &
      \memoryaddrs[(1)]{17em}
      \memory{1}{\mainpassc}
      \memory{1}{\mainsealc}
      \memory{1}{\retptrc}
%      \memory{1}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-18em}{0.75em}{5}
      \\
      {\tt 8} &
      \memoryaddrs[(0)]{12em}
      \memory{3}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-18em}{0.75em}{0}
      \\
      {\tt 20} &
      \memoryaddrs[(1)]{17em}
      \memory{1}{\mainsealc}[{\makebox[0pt]{S(0)}}]%
      \memory{1}{\mainpassc}[{\makebox[0pt]{P(0-1)}}]%
      \memory{1}{\retptrc}
%      \memory{1}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-18em}{0.75em}{0}
      \\
      {\tt 25} &
      \memoryaddrs[(1)]{17em}
      \memory{1}{\mainsealc}
      \memory{1}{\mainpassc}
      \memory{1}{\retptrc}
%      \memory{1}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-18em}{0.75em}{\bf 5}
\end{tabular}
\end{center}
\vspace{\abovedisplayskip}
\end{subfigure}
\caption{A violation with pass-by-reference}
\label{fig:passing}
\end{figure}

@@

\citet{SkorstengaardSTK} enumerate a useful list of criteria for judging
proposed stack safety properties: they should be (1) intuitive; (2)
useful for reasoning; (3) reusable in secure compiler chains; (4)
arguably ``complete;'' and (5) potentially scalable.  We believe our
approach competes well with theirs on criteria (1), (4), and (5).
Their approach is specifically set up to address (3), while
ours is not. Addressing (2) remains as future work for us.\apt{OK?}

%% Although there are some important differences between
%% \citeauthor{SkorstengaardSTK}'s properties and our own, the new
%% properties arguably satisfy their list of desiderata for such
%% formulations: notably, they reflect (and refine) programmer intuitions
%% about stack safety, furnish a comprehensive picture of the meaning of
%% stack safety, can be used to reason about program behavior, and are
%% flexible enough to be allow extensions to richer settings.
%% %
%% \sna{Some of this seems like more detail than we need, and we need to
%%   compare ourselves to their list of criteria.}
%% \rb{Trimmed this a bit. Are you referring to their list of attack
%%   examples, or to something else?\apt{Their list at start of section 4.
%%   \rb{Had a go at this.}}}
